Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed a few comments

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
However, past research 
has shown that both technical factors, which describe the commit
and the project receiving the commit, and social factors, which describe the
developer making the commit, have been found useful when predicting a
contribution's quality~\cite{tsay14icse,tsay14fse}.\todo{One or two more
  sentences, either here or earlier in the paragraph (between the first and
  second sentence), about why social factors might be interesting to study, or informative.}

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration. \todo{What's the
  difference, and why might it matter? Why is CI interesting or different as
  compared to pull requests?(one sentence or so).} Thus, we propose to analyze the
success every time a developer pushes a contribution to be built. 
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we can use the build integration status of the commit as documentation of
the commit's quality.

@@

Since we are interested in the success of the job status of each contribution, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
At this point 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\% if ran on the full data
set.

The high ratio of successful to not successful builds leads a naive classifier to 
favor misclassifying not successful\todo{everywhere you say ``not successful'',
  replace with ``unsuccessful''.} builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of not successful builds.  
We build this data set by copying over all not successful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, a process known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.

>>>>

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tasy14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration.  While pull requests
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors involved in continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we can use the build integration status of the commit as documentation of
the commit's quality.

@@

Since we are interested in the success of the job status of each contribution, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and unsuccessful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
At this point 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\% if ran on the full data
set.

The high ratio of successful to unsuccessful builds leads a naive classifier to 
favor misclassifying unsuccessful builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of unsuccessful builds.  
We build this data set by copying over all unsuccessful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, a process known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.
